\documentclass[a4,12pt]{article}

\usepackage{hyperref}

%-------------------------------------
\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-------------------------------------

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage[czech]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{titlesec}
\titleformat{\subsection}
  {\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

\titleformat{\section}
  {\LARGE\bfseries\filcenter}{\thesection}{1em}{}

\pagestyle{empty}

\begin{document}

\section*{Matúš Námešný}


\begin{center}
\href{mailto:matus@namesny.com}{matus@namesny.com} · www.namesny.com · \href{www.github.com/LordMathis}{github.com/LordMathis}
\end{center}

I am a fast learning and very motivated  Computer Science graduate. I have a strong knowledge base in Mathematics and Computer Science. I love problem solving and finding clean and elegant solutions. My interests include machine learning, web development and open source software.

%\hrulefill

\subsection*{Education}\label{education}

\begin{itemize}
\item
  \textbf{Masaryk University in Brno}, Faculty of Informatics\\
  Mater's degree in Artificial Inteligence and Natural Language Processing (2017 - 2019)
\item
  \textbf{Charles University in Prague}, Faculty of Mathematics and
  Physics\\
  Bachelor's degree in Computer Science (2013 - 2017)
\end{itemize}

\subsection*{Work Experience}\label{work}

\begin{itemize}
\item
  \textbf{R\&D Engineer} \hfill \textbf{Konica Minolta Laboratory Europe} \hfill (July 2018 - )
  \begin{itemize}
      \item Internship for Master's thesis: created a tool to predict age and gender from image data using neural networks
      \item Since August 2019 working full time as an R\&D Engineer
  \end{itemize}
\item
  \textbf{Internship} \hfill \textbf{Tieto} \hfill (February 2018 - April 2018)
  \begin{itemize}
      \item Deployed and administred OpenStack Orchestration with Heat
  \end{itemize}
\end{itemize}

\subsection*{Projects}\label{projects}

\begin{itemize}

\item
  \textbf{Personal Website} (\href{https://github.com/LordMathis/namesny.com}{https://github.com/LordMathis/namesny.com})
  
  My website is built with React and Node.js.

\item
  \textbf{FilmTit} (\href{https://www.github.com/LordMathis/FilmTit}{https://www.github.com/LordMathis/FilmTit})

  Movie subtitles web based editor with machine translation and
  translation memory. Part of my bachelor's thesis.
  
\item
    \textbf{Neural Network} (\href{https://github.com/LordMathis/ArtificialNeuralNetwork}{https://github.com/LordMathis/ArtificialNeuralNetwork})

    Java implementation of multilayer perceptron with mini-batch gradient descent, L2 regularization and momentum.

\end{itemize}

\subsection*{Skills}\label{skills}

\begin{itemize}
\tightlist
\item
  \textbf{Programming:} Python (TensorFlow, Keras), Java and Java EE, Javascript (React, Node.js)
\item
  \textbf{Other skills} git, Linux, Docker, OpenStack
\item
  \textbf{Foreign Languages:} English, French
\end{itemize}

\end{document}
